### 2022-04-25 background.tex
Add DEF-DL description

>>>>

To better solve the disadvantages of deep clustering, a new deep embedding clustering based algorithm DEF-DL~\cite{DEF-DL} is proposed.
DEF-DL uses supervised network to replace of K-means clustering algorithm, and use this feature as the input of uPIT network to separate speech.
The whole structure is as figure~\ref{fig:def_dl_structure}.
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{img/DEF-DL_structure}
    \caption{DEF-DL structure}
    \label{fig:def_dl_structure}
\end{figure}
